Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-06-14 Abstract Files/SCCAbstract_SDSS2022-knitr.Rnw
updates from conference talk

\section{Acknowledgements}
This material is based upon work supported by the National Science Foundation under Grant No. 1952007. We would also like to thank our collaborators at Iowa State, the Iowa League of Cities, and the various Iowa government organizations which publish their data at \url{data.iowa.gov}.

>>>>

\section{Acknowledgements}

### 2022-06-14 SDSS Presentation/SDSS Presentation.Rmd
updates from conference talk

---
# Rural Shrink Smart Project
.center[
<img src="images/Shrink_Smart_logo.png" width="35%"/>
]

@@

.center[
<img src="images/version1.png" width="80%"/>
]

@@

.center[
<img src="images/version2.png" width="52%"/>
]

@@

.center[
<img src="images/version3.png" width="60%"/>
]

@@

.center[
<img src="images/version4.png" width="75%"/>
]

>>>>

---
# Rural Shrink Smart Project
.center[
<img src="images/Shrink_Smart_Logo.png" width="35%"/>
]

@@

.center[
<img src="images/Version1.png" width="80%"/>
]

@@

.center[
<img src="images/Version2.png" width="52%"/>
]

@@

.center[
<img src="images/Version3.png" width="60%"/>
]

@@

.center[
<img src="images/Version4.png" width="75%"/>
]
